Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
improved

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes_lle}
\end{center}
\caption{\small{
Locally linear embedding (LLE) visualization of the codebook.
LLE tries to keep near neighbors (here according to euclidean distance)
in the same $2$D neighborhood. Shown patterns were randomly selected
in each neighborhood.
}
FIXME:Can we make this a little bit bigger so the patterns are
actually visible?  Does the figure add much over Fig \ref{fig:codes1}?
Maybe it has some more complex patterns? 
}
\label{fig:lle}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.8\columnwidth]{codes_8bars}
\end{center}
\caption{\small{Sample of longer codewords spanning over $8$ bars. Codewords
selected randomly from a codebook of size $200$. As usual, we see sustained
notes, but also some long-term structure.
FIXME: I (ronw) like the middle-left pattern, but I'm totally confused
by those in the top right and bottom row.  Are they ever used?  They
don't seem to be smoothed out at all, and are probably outliers
containing only one or two training points.
}}
\label{fig:codes8bars}
\end{figure}

>>>>

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes_lle}
\end{center}
\caption{\small{
Locally linear embedding (LLE) visualization of the codebook.
LLE tries to keep near neighbors (here according to euclidean distance)
in the same $2$D neighborhood. Shown patterns were randomly selected
in each neighborhood.
}}
\label{fig:lle}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.8\columnwidth]{codes_8bars}
\end{center}
\caption{\small{Sample of longer codewords spanning over $8$ bars. Codewords
selected randomly from the codewords used in the test set. Percentage of
used display in parentheses.
Most patterns are sustained notes, but codeword 0 shows a repeted two notes
pattern.
}}
\label{fig:codes8bars}
\end{figure}
